Title

### 2021-05-25 paper/main.tex
Tentative title
Basic MD paragraph on the GROMOS section

The SHAKE algorithm \cite{Ryckaert_1977} was employed to constrain all
bonds to their reference values with a relative tolerance of
$10^{-4}$, allowing for a time-step of 2 fs using the leapfrog
algorithm \cite{Hockney_1977}.
\subsubsection{NAMD}

>>>>

The SHAKE algorithm \cite{Ryckaert_1977} was employed to constrain all
bonds to their reference values with a relative tolerance of
$10^{-4}$, allowing for a time-step of 2 fs using the leapfrog
algorithm \cite{Hockney_1977}.  For water, the SPC model was used
\cite{Berendsen_1981}.  Non-bonded interactions were computed using a
triple range cut-off. Interactions within the short-range cut-off of
0.8 nm were computed every time-step, from a pair-list that was
generated every 5 steps.  At these time points, interactions between
0.8 and 1.4 nm were also computed which were kept constant between
these updates.  A reaction-field contribution was added to
electrostatic interactions approximating for a homogeneous medium
outside the 1.4 nm long-range cut-off, employing the relative
permittivity of SPC water (61) \cite{Tironi_1995}. All interactions
were calculated using the GROMOS 54a8 potential energy function, with
all graphene atoms modeled as neutral sp$^2$ carbons \cite{Reif_2012}.
After a steepest-descent minimization to remove bad contacts, all
velocities were randomly assigned from a Maxwell-Boltzmann
distribution at 298 K.  All simulations were run coupled to
thermostats using the weak-coupling algorithm
\cite{Berendsen_1984}. The solute, graphene and solvent atoms were
independently coupled to different heat baths. Additionally, the
graphene layer was coupled to separate baths for regulation of its
center of mass motion and its rotational and internal degrees of
freedom. This totaled 4 heat baths.

\subsubsection{NAMD}
